Semi-supervised author disambiguation of scientific publications

### 2015-07-20 paper.tex
problem statement

Before presenting the methodology, we need to define some terminologies we will
use to describe the data entities. An author's full name, or author name, is
the string variation that was mention in the database record to refer to the
author. The full name is a composition of the author last name and the author
other names. For example, in the full name (Kerth, Leroy T.), the last name is
Kerth and the other names will be (Leroy T.). We also use the terminology
initials. In our full name example, the initials will be (L T). First initial
then will be (L). So, grouping publications  What we refer to as the real
author is the real person behind the publication. We will use the term
signature as the entity that we apply clustering on.  A signature is a unique
combination between a publication and an author name as mentioned in the
database. The term blocking means grouping the signature by a certain version
of the author name. For example, blocking by the author last name and first
name initial means grouping together all signatures that have in common the
same author's last name and first name initial. In our example, grouping by the
string (Kerth L). What we mean by claimed publications is the publications in
which their real author identity were claimed. We use these claimed
publications to generate our ground truth data.

Our methodology consists in 4 main components: Distance learning, blocking,
semi-supervised clustering and matching. A distance function is learned from a
training set of signiture pairs sampled from ground-truth data. Each pair is
labeled whether the 2 signatures are for the same real author or not. The
learned distance function will then be used for computing the dissimilarity
matrix of a block of signatures. A block of signatures is grouping signatures
that have in common similar author names, for example same last name. This
affinity matrix would be the main input of our semi-supervised clustering
algorithm. The predicted clusters of each block will lastly be combined into a
final predicted clusters result. Each cluster label represents the predicted
single author of the publications in the cluster. Finally, we present a
strategy for matching the predicted results with the publications in which
their authors were claimed.

>>>>

Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
p_{N-1}\}$ and a set of authors ${\cal A} = \{ a_0, ..., a_{M-1}\}$
corresponding to individuals.  Let us define a signature $s \in p$ from a
publication as a unique piece of information identifying one of the authors of
$p$ (e.g., the author name, his affiliation, along with any other metadata can
be derived from $p$). Let us denote by ${\cal S} = \{ s | s \in p, p \in {\cal
P} \}$ the set of all signatures that can be extracted from all publications in
${\cal P}$. In this context, the author disambiguation problem can be stated as
the problem of finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of
${\cal S}$ such that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$
for all $i \neq j$, and where subsets $c_i$, or clusters, each corresponds to
the set of all signatures belonging to the same individual $a_i$. Note that in
practice, the set ${\cal A}$ often remains unknown and the task therefore boils
down to finding a partition ${\cal C}$ such that subsets   $c_i$  each
corresponds to the set of all signatures from a same individual.

% Before presenting the methodology, we need to define some terminologies we will
% use to describe the data entities. An author's full name, or author name, is
% the string variation that was mention in the database record to refer to the
% author. The full name is a composition of the author last name and the author
% other names. For example, in the full name (Kerth, Leroy T.), the last name is
% Kerth and the other names will be (Leroy T.). We also use the terminology
% initials. In our full name example, the initials will be (L T). First initial
% then will be (L). So, grouping publications  What we refer to as the real
% author is the real person behind the publication. We will use the term
% signature as the entity that we apply clustering on.  A signature is a unique
% combination between a publication and an author name as mentioned in the
% database. The term blocking means grouping the signature by a certain version
% of the author name. For example, blocking by the author last name and first
% name initial means grouping together all signatures that have in common the
% same author's last name and first name initial. In our example, grouping by the
% string (Kerth L). What we mean by claimed publications is the publications in
% which their real author identity were claimed. We use these claimed
% publications to generate our ground truth data.

% Our methodology consists in 4 main components: Distance learning, blocking,
% semi-supervised clustering and matching. A distance function is learned from a
% training set of signiture pairs sampled from ground-truth data. Each pair is
% labeled whether the 2 signatures are for the same real author or not. The
% learned distance function will then be used for computing the dissimilarity
% matrix of a block of signatures. A block of signatures is grouping signatures
% that have in common similar author names, for example same last name. This
% affinity matrix would be the main input of our semi-supervised clustering
% algorithm. The predicted clusters of each block will lastly be combined into a
% final predicted clusters result. Each cluster label represents the predicted
% single author of the publications in the cluster. Finally, we present a
% strategy for matching the predicted results with the publications in which
% their authors were claimed.
